\documentclass[letter,10.9pt]{article}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\hyphenation{Inte-lligent}

\usepackage{url}

\raggedbottom
\raggedright
\usepackage{tocloft}
\usepackage{parskip}

\usepackage[T1]{fontenc}

\usepackage{graphicx}

\usepackage[space]{xeCJK}

%%% Assuming Chinese is the main CJK language...
\setCJKmainfont[
  BoldFont=WenQuanYi Zen Hei,
  ItalicFont=AR PL KaitiM GB]
  {AR PL SungtiL GB}
\setCJKsansfont{Noto Sans CJK SC}
\setCJKmonofont{cwTeXFangSong}

\pagestyle{empty}

\makeatletter
\renewcommand{\section}{\@startsection
  {section}
  {12}
  {\z@}
  {0.1\baselineskip}
  {0.1\baselineskip}
  {\ruled@title}}
\newcommand{\ruled@title}[1]{
  \normalfont\large\scshape\bfseries #1\vskip2pt\hrule\vspace{0pt}}
\makeatother

\newcommand*{\Cdot}{\raisebox{-1.3ex}{\scalebox{4}{$\mathbf{\cdot}$}}}

\newcommand{\restitle}[4]{
  \begin{center}
    {\bfseries\scshape\Large #1}\\
    \vspace{3pt}
    #2\\
    #3\\
    #4
  \end{center}
}

\newcommand{\resentryedu}[4]{
  \begin{minipage}[t]{\linewidth}
    \setlength\tabcolsep{0pt}
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} - #2 & #3 
    \end{tabular*}
    
    #4
  \end{minipage}
}


\newcommand{\resentry}[4]{
  \begin{minipage}[t]{\linewidth}
    \setlength\tabcolsep{0pt}
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} - #2 & #3 \\
    \end{tabular*}
    \rule{3pt}{0pt}
	#4
  \end{minipage}
}

\newcommand{\resentryproj}[5]{
  \begin{minipage}[t]{\linewidth}
    \setlength\tabcolsep{0pt}
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} #2 - #3 & #4 \\
    \end{tabular*}
    \rule{3pt}{0pt}
	#5
  \end{minipage}
}

\newcommand{\resentrysimple}[3]{
  \begin{minipage}[t]{\linewidth}
    \setlength\tabcolsep{0pt}
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} & #2 \\
    \end{tabular*}
    \rule{3pt}{0pt}
	#3
  \end{minipage}
}


\newcommand{\resentryhonor}[2]{
  \hspace{1pt}\labelitemi\hspace{4pt}#1\hfill #2 \\
  \vspace{2pt}
}

\newcommand{\resentryadd}[2]{
  \textbf{#1}: #2 \\
  \vspace{2pt}
}

\newcommand{\resproject}[1]
{Project: \textquotedbl\textsf{\slshape#1}\textquotedbl}

\newenvironment{resitemize}
{\vspace{-10pt}
\begin{itemize}
\setlength{\parskip}{0ex}
\setlength{\leftskip}{-14pt}}
{\end{itemize}}

\newenvironment{resitemizeempty}
{\vspace{-10pt}
\renewcommand\labelitemi{}
\begin{itemize}
\setlength{\parskip}{0ex}
\setlength{\leftskip}{-19pt}}
{\end{itemize}}

\begin{document}

\restitle{Jiayi Zhou}
{Email: judyzhou959@utexas.edu | Cell Phone: (571)\ 269-9367 }{LinkedIn:www.linkedin.com/in/jiayi-zhou-utexas}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EDUCATION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resentry
{The University of Texas at Austin }
{Austin, TX}
{Expected May 2021}
{
\begin{resitemize}
\item BS in Computer Science | GPA: 3.89/4.00
\item Coursework: Principles of Computer Systems, Algorithms and Complexity, Computer Organization And Architecture, Python, Java, Data Structure, Discrete Math, Introduction to Probability and Statistics
\item Natural Sciences College Scholar 2018
\item University Honors (Spring 2018; Spring 2017; Fall 2017)
\end{resitemize}
 }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EXPERIENCE}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resentry
{Deep Brain Research}
{\emph{Undergraduate Research Assistant}; Austin, TX}
{August 2018 - December 2018}
{
\begin{resitemize}
\item Developed virtual environments to test different navigation models in the human brain through simulated spatial navigation tasks.
\item  Scripting C\# to designing and programming virtual environments within the Unity game engine. 
\end{resitemize}
 }
 
\resentry
{Mobike}
{\emph{Data Analyst Intern - TECH-Big Data/BI Group}; Beijing,China}
{May 2018 - August 2018}
{
\begin{resitemize}
\item Built, developed and maintained tables in overall data mart by writing SQL queries and shell scripts.
\item Programmed complex SQL queries across large volumes of data on datasets (Hadoop, MySql) for data mining, cleaning and munging. 
\item Used Mobike’s internal data visualization tool (similar to Tableau) to create visualizations, and interactive dashboards.
\item Analyzed users' behaviors that should be tracked for company’s analytical requirements. Designed a data tracking PRD(Product Requirement Documentation) for technical team  based on Event Recording Model. Programmed Hive SQL queries to cleanse and normalize collected raw data into high-quality aligned with company’s analytical requirements
\item Conducted data analysis with Excel(pivot table, vlookup) for PM team and International Strategy team in order to evaluate, identify, and implement actionable business performance measures.
\item Used Python, Pandas, and Numpy to cleanse and manipulate raw data.
\end{resitemize}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PROJECTS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resentryproj
{Art Gallery}
{}
{Unity3D project}
{Fall 2018}
{
\begin{resitemize}
\item Created 3D environment for studying spatial navigation. Current level: control player's view by mouse; control player's movement by keyboards; the door will be open after player correctly matching same pictures on the wall.
\end{resitemize}
}
 
\resentryproj
{Random Writer}
{}
{Python project}
{Fall 2018}
{
\begin{resitemize}
\item Used a Markov chain to create a statistical model of a piece of English text or bytes. Simulate the Markov chain to generate stylized pseudo-random text. 
\end{resitemize}
}
 
\resentryproj
{Pricing Strategy Project}
{}
{Data Analysis}
{Summer 2018}
{
\begin{resitemize}
\item Analyzed data of trips and of membership card from all Mobike's oversea users by using Excel; Provided advice for new pricing strategy; increased income and gained more users.
\end{resitemize}

\resentryproj
{Huffman Coding}
{}
{Data structure project}
{Spring 2018}
{
\begin{resitemize}
\item A processor to compress and uncompress data based on Huffman's algorith: .txt and .html files could be compressed by 40\%; .gz, .bz, .zip, .rar could be compressed by 43\%; .tif could be compressed 18\%
\end{resitemize}
}

\resentryproj
{Graph Algorithms}
{}
{Java project}
{Spring 2018}
{
\begin{resitemize}
\item Modeled a directed, weighted graph to rank college football teams for a given season based on wins and margin of victory. Find all weighted shortest paths from the starting vertex to all other vertices in this Graph using Dijkstra's algorithm.
\end{resitemize}
}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SKILLS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{12pt}
\begin{resitemize}
\item Programming Languages: Java, SQL, Python, C, C\#
\item Software: Eclipse, MySQLWorkbench, Visual Studio, Unity, Jupyter Notebook, Excel
\item Languages: Chinese(Native), English(Fluent), Korean(Basic)
\end{resitemize}
\vspace{8pt}

\end{document}